\documentclass[report.tex]{subfiles}
\begin{document}
\newpage
\begin{large}
\section{INTRODUCTION}
    % what is the program
    Logic circuits are one of the core components of CPUs. These circuits allow manipulating binary data and carrying out various logical operations.
    Programs such as Proteus and Logisim can be used to simulate logic circuits.
    For our project, we decided to create a similar (albeit heavily simplified) logic simulator named \textbf{MinimaLogic}.
    \\\\
    \textbf{MinimaLogic} is a GUI based logic simulator that allows simulation of various logic gates and circuits.
    It allows users to create and simulate circuits ranging from a simple 1-bit adder to more complex circuits like 4-bit counters.
    In fact, one could create any circuit that fits within the available area using the components provided in the program.
    The program allows the user to interact via mouse and keyboard. To make the program user friendly, we tried to keep the controls as intuitive as possible.
    \\\\
    This program heavily relies on the Simple DirectMedia Layer(SDL2) Library for GUI elements as well as user interation/input. 
    Alongside SDL2, the program also utilizes SDL2\_ttf for font rendering as well as the Windows API for opening/saving files.
    Other standard headers that are available with all modern development environments have also been used.
    % describe a little bit about C
    \subsection{The C language}
    % describe program structure
    \subsection{Structure of Code}
    % describe a little about SDL
    % SDL program loop
    \subsection{Simple DirectMedia Layer(SDL2)}
    Simple DirectMedia Layer is a cross-platform development library designed to pro-
    vide low level access to audio, keyboard, mouse, joystick, and graphics hardware
    via OpenGL and Direct3D. It is used by video playback software, emulators, and
    popular games including Valve’s award winning catalog and many Humble Bundle
    games.\\\\
    SDL2 libraries also contains extension to keep SDL as light as possible. Some of the
    libraries are SDL2\_image,SDL2\_net,SDL2\_mixer,SDL2\_ttf, true type SDL2\_rtf.SDL2\_image
    is used to load different images,SDL2\_net is used for cross platform networking
    , SDL2\_mixer is an audio mixer library that supports WAV,MP3,MIDI and OGG.
    SDL2\_ttf is used to write using fonts in the program and SDL2\_rtf is Rich Text Format
    library. Out of these libraries, we only used SDL2\_ttf.
    \\\\
    The SDL2 library is more oriented towards game development and it provides a vast quantity of features such as 3D rendering, hardware accelerated 2D graphics, multiple windows, multiple audio devices, multiple input devices etc. 
    Since our program is much simpler than a full fledged game, We were only able to utilize a small fraction of SDL's features.
\end{large}
\end{document}
